A Case Study in Preserving a High Energy Physics Application

### 2014-03-02 paper.tex
modify section 4: one implementation using parrot

Table~\ref{table:archive-map} illustrates the structure of the remote archive.
{\tt /archive/OS} includes the images of different Operating Systems.
{\tt /archive/software} integrates all the commonly used software, such as git,
python, perl. The archive also organizes the data from CMSSW, Git, HTTP and the
Grid. {\tt /archive/experiment} includes the all the experiments submitted into the
archive. The private files and description files of each experiment will be
organized together.

The Version 4 of Table~\ref{table:scripts} illustrates the script used in
Solution 4, which is the same as the one used in Solution 3. 
However, one map file is necessary for the relocation of the data access targets, as
show in Figure~\ref{fig:version-evolution}. 
The map file redirects the git access path into {\tt /archive/git} from the original path (\path{http://github.com}) referred in the script.
This design decouples the experiment script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
and ensures the transparent access.
The modification of the archive only introduces the minimal changes of the map file.

The archive supports two different data preservation model: Internal and External. Internal method will preserve the data in the archive. External method refuses to preserve the content of data, but only preserve the reference to the actual storage place of data. For example, the size of experiment data from the Grid is extremely large, and storing the same data in the archive is time-consuming and space-consuming. Through External method, the archive only preserves one reference to the data inside the remote Grid.

This solution tries to create one self-contained and independent package for each experiment and integrate different packages for different experiments into one archive to multiplex common data. One packaging utility  will be provided to help the original author to generate the package. The archive can maintain the experiment dependencies through Internal or External method. The archive itself will be responsible for the data maintenance and relevant authority access problem. All the new user can repeat one experiment through the interaction with the archive.

@@

With the help of Parrot, one packaging utility which generates one independent
package for one program to make the reproduction of the program convenient can
be deployed. The starting point of the packaging utility is one successful execution
sandbox (the data from grid has been preserved in HDFS and the software from
CMSSW, Git and HTTP has been on the local machine.). We re-execute the actual
data analysis code under Parrot and get the name list of all the files actually
accessed during the execution process of the actual data analysis. Then,
according to the file name list, one package containing all the necessary data
and software for one analysis program is generated. Next time, when another
scholar wants to repeat the program, he only needs to obtain the package and
directly execute the actual analysis program inside the package.

@@

The shell script of the Solution 2 is simplified into one new version, which
only contains the necessary environment variables and the
actual analysis command. Table~\ref{table:parrot-script} illustrates
the simplified script.

@@

Figure~\ref{fig:workflow-parrot} illustrates the workflow of this solution.

The workflow of generating one package for one analysis program is as follows.

@@

Parrot is one virtual file system that can support user access to multiple underlying file systems. Parrot traps each system call involved in the process of data access, figures out the type of file system and redirects it into corresponding operations to the accessed file system. During this process, each accessed file is recorded into one file with the access type of it, such as open, stat, read and write.

The command used to generate the file name list is as follows. The {\tt -L} parameter refers to the path of the file containing all the accessed file name of the experiment.

@@

The original ouput of this command is one namelist file with the size of 6.6MB
and 132,058 lines, each of which corresponds to one one accessed file of the
program. We noticed that some items appeared multiple times. To reduce the
packaging time, de-duplication and sorting techoniques are used for the
namelist file, generating one smaller file with the size of 3.2MB and 67,178 lines.

@@

The packaging utility iterates each filename inside L1 and copies it into the
target package. After finishing the packaging process, the target package
together with its description information, and one map file, which redirects
the access of files from different file systems into the files inside the target package, will be
provided to users. The packaging process also runs within Parrot environment to
access data from different file systems.

\begin{figure}
\centering
\epsfig{file=package-info.eps, height=1.2in, width=2.5in}
\caption{Package Description Infomation}
\label{fig:package-info}
\end{figure}
The command used to generate the package containing all the files of L1 is as follows. 
{\tt package-utility.sh} is a bash script which iterates each line of L1 and
determines the behavior according to the file type (common files, directories,
linked files) and the system call type.
The package description information is shown in Figure~\ref{fig:package-info}.

@@

%*****lack: file content + metadata; only file metadata; different process
%solutions
Each file inside L1 is copied into the package, the final path of the file
becomes the path of the package, followed by the original file path. In this
program, the path of the package is {\tt /tmp/package-hep}, so the final path of one
file with the original path path1 is {\tt /tmp/package-hep/path1}.

To ensure the successful reproduction, the filesystem structure of the original
execution environment should be preserved as completely as possible. However,
attempting to copy the whole content of one directory or one file is
space-consuming and time-consuming, because the original program may only
access the metadata of one file with the size of 200GB. Our solution is to
determine the copy degree of one directory or one common file according to the
system call type for its path.

The map relationship between the file access path used in the actual analysis
program and the actual file location used during the reproduction process is
kept inside the map file. The structure of the map file is shown in Table~\ref{table:map-file}.

@@

When another scholar wants to repeat one analysis program, the accessed data
field is limited into the target package with the help of the map file 
generated in step 2.

Command:

@@

The map file of one package supports pattern matching semantics,
which greatly reduces the scale of the map file and improves the efficiency of file path redirection. 
For example,
one item inside the map file is {\tt /dir1 /package-dir1} means that the access to each file and
subdirectory under {\tt /dir1} will be redirected into {\tt /package-dir1}.
If the semantics of the map file do not support pattern matching, the size of the map file will become astonishing. 
{\tt /dir1} may contain thousands of files, which will generates thousands of map items and will take more time to redirect file paths.

During the packaging process, we noticed
that it is impossible to copy the files under certain directories.
For example, during namelist acquisition process, three special files under {\tt /dev} directory were recorded into the namelist: tty, null and urandom, which are used for input and output.
We tried to copy these files into the new package, but the packaging utility halted.
We also noticed that copying the files under directories like {\tt /proc} is
meaningless. Because the process id of one program is random and depends on the
current allocation of process ID.

As for these two file categories, letting
the program directly utilize the files on the machine, where the new user
repeats the program, is a better choice. The semantics is implemented by
setting the target path of one file equal to the origin file path inside the
map file. For example, {\tt /dev /dev} means that when the program needs to access
files under {\tt /dev} directory, it will directly use the file under {\tt /dev}, which is
independent from the namespace of the package. This semantics also makes the
reference of files outside the package possible. If the new user wants to
expand the analysis of one program to his own data with the path of {\tt /A}, he can add the analysis
code into the analysis script and add one item {\tt /A /A} into the map file.

@@

Under Solution 4, the reproduction of one analysis program becomes easier.
Rethink Matthias's example, the reproduction of it only needs
the necessary environment variables, the actual analysis command
and the package. If different scholars want to repeat one analysis program,
what they need to do is to obtain the package and rerun the actual analysis
program. Under Solution 2, each scholar needs to get the necessary data and
software, and then prepare software environment.

%here is the new content-hmeng
The starting point of Solution 4 is one successful execution sandbox on the original machine. 
Parrot traps all the system calls and copies each accessed file (except for common dependencies) into one package.
The necessary scientific data will be copied into the target package.
The software dependencies can be divided into two categories: clear dependencies, which can be observed directly through reading the analysis script and implicit dependencies,
which can not be obtained through reading the analysis script. 
Parrot can obtain every dependency through trapping each system call.
Strictly speaking, the software concept and the scientific data concept are lost in Solution 4, because
the granularity of parrot is file.
The same thing happens to networked resources.
Packaging utlity maintains one list of common dependencies and first judges whether the file belongs to this list before trying to copy one file into the package.
As for the computing environment, Solution 4 notices the new user through the description information at the beginning of the script.
%the following subsection belongs to the "discussion of data and software
%preservation" section

>>>>

Table~\ref{table:archive-map} illustrates the structure of the remote archive.
Item {\tt /archive/OS} includes the images of different Operating Systems.
Item {\tt /archive/software} integrates all the commonly used software, such as git,
python, perl. The archive also organizes the data from CMSSW, Git, HTTP and the
Grid. Item {\tt /archive/experiment} includes the all the experiments submitted into the
archive. The private files and description files of each experiment will be
organized together.

The Version 4 of Table~\ref{table:scripts} illustrates the script used in
Solution 4, which is the same as the one used in Solution 3. 
However, one map file is necessary for the relocation of the data access targets, as
show in Figure~\ref{fig:version-evolution}. 
The map file redirects the git access path into {\tt /archive/git} from the original path (\path{http://github.com}) referred in the script.
This design decouples the experiment script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
and ensures the transparent access.
The modification of the archive only introduces the minimal changes of the map file on the client side.

The archive supports two different data preservation models: Internal and External. Internal method will preserve the data in the archive. External method refuses to preserve the content of data, but only preserve the reference to the actual storage place of data. For example, the size of experiment data from the Grid is extremely large, and storing the same data in the archive is time-consuming and space-consuming. Through External method, the archive only preserves one reference to the data inside the remote Grid.

This solution tries to create one self-contained and independent package for
each experiment and integrate different packages for different experiments into
one archive to multiplex common data. One packaging utility, which can figure out all the really used data of one program  will be provided
to help the original author to generate the package. The archive can maintain
the experiment dependencies through Internal or External method. The archive
itself will be responsible for the data maintenance and relevant authority
access problem. The new user can repeat one experiment through the
interaction with the archive.

@@

With the help of Parrot, one packaging utility which generates one independent
package for one program to make the reproduction of the program convenient can
be deployed. The starting point of the packaging utility is one successful execution
sandbox (the data from grid has been preserved in HDFS and the software from
CMSSW, Git and HTTP has been on the local machine.). We re-execute the actual
data analysis code under Parrot and get the name list of all the files actually
accessed during the execution process of the actual data analysis. Then,
according to the filename list, one package containing all the necessary data
and software for one analysis program is generated. Next time, when another
scholar wants to repeat the program, he only needs to obtain the package and
directly execute the actual analysis program inside the package. 
Figure~\ref{fig:solution3} illustrates the working principle of the packaging utility.

@@

Table~\ref{table:parrot-script} illustrates
the simplified script, which
only contains the necessary environment variables and the
actual analysis command.

@@

Figure~\ref{fig:workflow-parrot} illustrates the workflow of this solution. Firstly, execute the analysis program under Parrot and obtain one filename list containing all the accessed files. Then generate one package containing all the files included in the filename list. Finally, rerun the program with the help of the package. Each step will be examined in details.

@@

Parrot is one virtual file system that can support user access to multiple
underlying file systems. Parrot traps each system call involved in the process
of data access, figures out the type of file system and redirects it into
corresponding operations to the accessed file system. During this process, each
accessed file, together with the access type, such as
open, stat, read and write, is recorded into one file.

The command used to generate the filename list is as follows. The {\tt -L} parameter refers to the path of the file containing all the accessed file name of the experiment.

@@

The original ouput of this command is one namelist file with the size of 6.6MB
and 132,058 lines, each of which corresponds to one one accessed file of the
program. We noticed that some items appeared multiple times in the filename list. To reduce the
packaging time, de-duplication and sorting techoniques are used for the
namelist file, generating one smaller file with the size of 3.2MB and 67,178 lines.

@@

The packaging utility iterates each filename inside L1 and copies it into the
target package. Finally, the target package
together with its description information, and one map file, which redirects
the access of files from different file systems into the files inside the target package, will be
generated as the output of this step. The packaging process also runs within Parrot environment to
access data from different file systems.

\begin{figure}
\centering
\epsfig{file=package-info.eps, height=1.2in, width=2.5in}
\caption{Package Description Infomation}
\label{fig:package-info}
\end{figure}
The command used to generate the package is as follows. 
{\tt package-utility.sh} is a bash script which iterates each line of L1 and
determines the behavior according to the file type (common files, directories,
symbolic link files) and the system call type.
The package description information is shown in Figure~\ref{fig:package-info}.

@@

%*****lack: file content + metadata; only file metadata; different process
%solutions
Each file inside L1 except for common dependencies is copied into the package, the final path of the file
becomes the path of the package, followed by the original file path. In this
program, the path of the package is {\tt /tmp/package-hep}, so the final path of one
file with the original path path1 is {\tt /tmp/package-hep/path1}.

The map relationship between the file access path used in the actual analysis
program and the actual file location used during the reproduction process is
kept inside the map file, as illustrated in Table~\ref{table:map-file}.

To ensure the successful reproduction, the filesystem structure of the original
execution environment should be preserved as completely as possible. However,
attempting to copy the whole content of one directory or one file is
space-consuming and time-consuming, because the original program may only
access the metadata of one file with the size of 200GB. Our solution is to
determine the copy degree of one directory or one common file according to the
type of the system call.

@@

When another scholar wants to repeat the analysis program, 
the description of the exepriment environment is firstly referred to build the underlying OS and basic software environment. In this example, the only necessary software basis is Parrot. Then the scholar can obtain one copy of the package and its map file, and rerun the program using the following command:

@@

The map file of one package supports pattern matching semantics,
which greatly reduces the scale of the map file and improves the efficiency of file path redirection. 
For example,
one item inside the map file is {\tt /dir1 /package-dir1} means that the access to each file and
subdirectory under {\tt /dir1} will be redirected into {\tt /package-dir1}.
If the semantics of the map file do not support pattern matching, the size of the map file will become astonishing. 
{\tt /dir1} may contain thousands of files, which will generate thousands of map items and take more time to redirect file paths.

During the packaging process, we notice
that it is impossible to copy the files under certain directories.
For example, during namelist acquisition process, three special files under {\tt /dev} directory were recorded into the namelist: tty, null and urandom, which are used for input and output.
Trying to copy these files into the new package would cause the packaging utility halt.
We also notice that copying the files under directories like {\tt /proc} is
meaningless. Because the process id of one program is random and depends on the
current allocation of process ID.

As for these special file paths, letting
the program directly utilize the files on the new machine, where the new user
repeats the program, is a better choice. The semantics is implemented by
setting the target path of one file equal to the origin file path inside the
map file. For example, {\tt /dev /dev} means that when the program needs to access
files under {\tt /dev} directory, it will directly use the file under {\tt /dev} on the new machine, which is
independent from the namespace of the package. This semantics also make the
reference of files outside the package possible. If the new user wants to
expand the analysis of one program to his own data with the path of {\tt /A}, he can add the analysis
code into the analysis script and add one item {\tt /A /A} into the map file.

@@

Under Solution 4, the reproduction of one analysis program becomes easier.
Rethink Matthias's example, the reproduction only needs
to set necessary environment variables, the actual analysis command
and the package. If different scholars want to repeat one analysis program,
what they need to do is to obtain the package and rerun the actual analysis
program. Under Solution 2, each scholar needs to get the necessary data and
software, and then prepare software environment.

%here is the new content-hmeng
The starting point of Solution 4 is one successful execution on the original machine. 
Parrot traps all the system calls and copies each accessed file (except for common dependencies) into one package.
The necessary scientific data and software dependencies will be copied into the target package.
Strictly speaking, the concept of software and the concept of the scientific data are lost in Solution 4, because
the granularity of parrot is file.
The same thing happens to networked resources.
Packaging utlity maintains one list of common dependencies and first judges whether the file belongs to this list before trying to copy one file into the package.
%the following subsection belongs to the "discussion of data and software
%preservation" section
